Fast Sorting on Modern Computers

### 2005-06-23 docs/tech_report/background.tex
fixed some TODOs

An algorithm which is $O(N)$ is said to complete in linear time. An algorithm
which is $O(N^2)$ is said to complete in quadratic time.  $O(NlogN)$ algorithms
may take several orders of magnitude more time than $O(N)$ algorithms, and
typically use the \n{divide-and-conquer} principle, or use a binary tree to
reduce complexity. Quicksort, mergesort and heapsort are all of this type,
whereas elementary sorts, such as insertion sort, selection sort, bubblesort and
shakersort are $O(N^2)$ algorithms. Radixsort is $O(N)$, but can be more
expensive than quicksort, due to the cost of each step.  These are discussed in
later chapters.
%TODO what's shellsort in Big O notation
TODO what's shellsort in Big O notation

An important thing to note is that the time the algorithms take to execute are
proportion to their Order, but different constants of proportionality are used
for different algorithms. An algorithm with $10N$ instructions is $O(N)$, and is
not differentiated from an algorithm with $1000N$ instructions by this
notation.

>>>>

An algorithm which is $O(N)$ is said to complete in linear time. An algorithm
which is $O(N^2)$ is said to complete in quadratic time.  $O(NlogN)$ algorithms
may take several orders of magnitude more time than $O(N)$ algorithms, and
typically use the \n{divide-and-conquer} principle, or use a binary tree to
reduce complexity. Quicksort, mergesort and heapsort are all of this type,
whereas elementary sorts, such as insertion sort, selection sort, bubblesort and
shakersort are $O(N^2)$ algorithms. Radixsort is $O(N)$, but can be more
expensive than quicksort, due to the cost of each step. These are discussed in
later chapters.

Not all algorithms have an easily derivable complexity. Many studies have
attempted to tie down the complexity of shellsort, and it is not easily
definable in terms of the catageories above (see \ref{TODO}).

An important thing to note is that the time the algorithms take to execute are
proportion to their complexity, but different constants of proportionality are
used for different algorithms. An algorithm with $10N$ instructions is $O(N)$,
and is not differentiated from an algorithm with $1000N$ instructions by this
notation.

### 2005-06-23 docs/tech_report/intro.tex
fixed some TODOs

Chapters \ref{heap} through \ref{quick} discuss base algorithms and cache-conscious improvements
for heapsort, mergesort and quicksort. Results are presented and explained, and
branch prediction implications of the changes are discussed.

Chapter \ref{radix} presents a radixsort implementation and discusses its performance in
the areas of instruction count, cache-consciousness and branch prediction.

%TODO shell
TODO Chapter \ref{shell}

>>>>

Chapters \ref{heap} through \ref{radix} discuss base algorithms and cache-conscious improvements
for heapsort, mergesort and quicksort. Results are presented and explained, and
branch prediction implications of the changes are discussed.

Chapter \ref{shell} presents two shellsort implementations and discusses their
performance in the areas of instruction count, cache-consciousness and branch
prediction.
